Refinements for open automata

### 2023-06-13 2021-Refinement/paper/refinementarticleV2.tex
visio

We define several variants of refinement relations between systems including either equal or different sets of holes, and 
show under which conditions these refinements are preserved by composition of open automata.

\keywords{Labelled transition systems  \and Refinement \and Composition.}
\end{abstract}
%
%
%
\section{Introduction}

\TODO{TODO list}

* \st{example a terminer}

* choisir terminologie: refinement or simulation

* \st{open automata  / Open Automata -> only use open automata or OA.}

* positioning

* \st{format according to conf: lncs FACS or SEFM}

* global rewriting (partly done)

The present trend in software engineering is towards component-based design. Compositional design is a highly convenient approach 
for specifying and verifying large systems. Automata are the basic formalism for this approach, but most automata definitions allow only the specifications of finite closed systems. Indeed those systems are the ones we can verify efficiently, but programming often consists in writing open systems that should be interfaced with others, and with potentially unbound behaviours (at least statically). We investigate in our works the possibility to define open symbolic systems, verify some of their properties, and use them to compose in a structured way more complex systems.

@@

\begin{property}[Relating simulations]\label{lem-sim-sim}
Hole-equal simulation is a particular case of hole-tracking refinement when  $J_1=J_2=H$.
\end{property}
\begin{example} Consider the automata of examples \ref{Example:fifo-system} and \ref{example:fifo-system-one}. As we saw above, \texttt{prod-cons} $\leq$ \texttt{simprod-cons}, therefore \texttt{prod-cons} $\leq_{\{\texttt{P,Q}\}}$ \texttt{simprod-cons}.
\end{example}
\TODO{potential ex 4: check if the example with a hole filled is a simulation of the example with holes? at least state \texttt{prod-cons} $\leq_{\{\texttt{P,Q}\}}$ \texttt{simprod-cons}}

@@

Consequently, as the simulation is transitive \TODO{TODO Thm 4}
We can state the following theorem: 
\begin{theorem}[Composability]\label{thm:Composability}
Let $A_1$, $A_2$, $A_3$ and $A_4$ be four OA with $\wrel{A_1}{A_2}{H}$ and $\wrel{A_3}{A_4}{H'}$.  Suppose that \(k \in H\). We have: \[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_4}{k}}{ H \uplus H'\setminus \mbrc{k}}\]
\end{theorem}

>>>>

We define refinement relations between systems including either equal or different sets of holes, and 
show under which conditions these refinements are preserved by composition of open automata.

\keywords{Labelled transition systems  \and Refinement \and Composition.}
\end{abstract}
%
%
%
\section{Introduction}
%
%
%\TODO{TODO list}
%
%
%* \st{example a terminer}
%
%* choisir terminologie: refinement or simulation
%
%* \st{open automata  / Open Automata -> only use open automata or OA.}
%
%* positioning
%
%* \st{format according to conf: lncs FACS or SEFM}
%
%* global rewriting (partly done)

\TODO{intro}
The present trend in software engineering is towards component-based design. Compositional design is a highly convenient approach 
for specifying and verifying large systems. Automata are the basic formalism for this approach, but most automata definitions allow only the specifications of finite closed systems. Indeed those systems are the ones we can verify efficiently, but programming often consists in writing open systems that should be interfaced with others, and with potentially unbound behaviours (at least statically). We investigate in our works the possibility to define open symbolic systems, verify some of their properties, and use them to compose in a structured way more complex systems.

@@

\begin{property}[Relating simulations]\label{lem-sim-sim}
Hole-equal simulation is a particular case of hole-tracking refinement when  $J_1=J_2=H$.
\end{property}
\begin{example} Consider the automata of examples \ref{Example:fifo-system} and \ref{example:fifo-system-one}. As we saw above, \texttt{prod-cons} $\leq$ \texttt{simprod-cons}, therefore \texttt{prod-cons} $\leq_{\{\texttt{P,Q}\}}$ \texttt{simprod-cons}.
\end{example}
%\TODO{potential ex 4: check if the example with a hole filled is a simulation of the example with holes? }

@@

Consequently, as the simulation is transitive we can compose the previous theorems and  state the following: 
\begin{theorem}[Composability]\label{thm:Composability}
Let $A_1$, $A_2$, $A_3$ and $A_4$ be four OA with $\wrel{A_1}{A_2}{H}$ and $\wrel{A_3}{A_4}{H'}$.  Suppose that \(k \in H\). We have: \[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_4}{k}}{ H \uplus H'\setminus \mbrc{k}}\]
\end{theorem}
